Initial Analysis

### 2019-09-09 Initial_Analysis.Rmd
Included a missing headding
Updates results

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  "EBImage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase" # for species ecosystem affinity
)

@@

### Sub Routine

@@

```
### Function `GetSppDist`

@@

### Function `EstTransIndex`

#### NOTES:

##### General:
- For now using SAU_C as presence absence
- Grouping by species distribution within EEZ and not EEZ area

##### Tresholds:
##### Model Index, line ~479

@@

##### Distribution Index, line ~482

@@

@@

## Routine for estimating transboundary species

@@

@@

```{r Routine_parallel, eval = F, echo = F}

@@

@@

@@

# Transboundary Results ####

# For Carmelia
if(Sys.info()[7] == "carmelia"){
  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
}else{

  # For Hall and The Beast

  Spp <- list.files(Results_Path)[1:672]

  Results_Trans <- GetTransResults(Spp)

  # Clean out countries that share with their own borders

  Auto_Remove_Territories <- Results_Trans %>%   
    rename(FishingRegion=Country_Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Country_Territory= FishingRegion,
           FishingRegion=Neighbour_Territory,
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour_Territory = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour_Territory),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  Territories_to_Remove <- Results_Trans %>% 
    filter(
      Country_Territory %in% Islands_to_Remove |
        Neighbour_Territory %in% Islands_to_Remove |
        Country_Territory == "Balearic Island (Spain)" & Neighbour_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
        Country_Territory == "British Virgin Isl. (UK)" & Neighbour_Territory == "Anguilla" |
        Neighbour_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
        Country_Territory == "Corsica (France)" & Neighbour_Territory == "France (Mediterranean)" |
        Neighbour_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
        Country_Territory == "Crete (Greece)" & Neighbour_Territory == "Grece" |
        Neighbour_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
        Country_Territory == "Cyprus (North)" & Neighbour_Territory == "Cyprus (South)" |
        Neighbour_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
        Country_Territory == "Channel Isl. (UK)" & Neighbour_Territory == "United Kingdom" |
        Neighbour_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
        Country_Territory == "Glorieuse Islands (France)" & Neighbour_Territory == "Mayotte (France)" |
        Neighbour_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
        Country_Territory == "Guam (USA)" & Neighbour_Territory == "Northern Marianas (USA)" |
        Neighbour_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
        Country_Territory == "Italy" & Neighbour_Territory == "Sardinia (Italy)" |
        Neighbour_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
        Country_Territory == "Italy" & Neighbour_Territory == "Sicily (Italy)" |
        Neighbour_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (main islands)"|
        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
        Country_Territory == "Japan (Daito Islands)" & Neighbour_Territory == "Japan (Ogasawara Islands)"|
        Neighbour_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
        Country_Territory == "Norway" & Neighbour_Territory == "Svalbard Isl. (Norway)" |
        Neighbour_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
        Country_Territory == "Sicily (Italy)" & Neighbour_Territory == "Sardinia (Italy)" |
        Neighbour_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
        Country_Territory == "South Africa (Atlantic Coast)" & Neighbour_Territory == "South Africa (Indian Ocean Coast)" |
        Neighbour_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
        Country_Territory == "USA (Alaska, Arctic)" & Neighbour_Territory == "USA (Alaska, Subarctic)" |
        Neighbour_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Country_Territory,Neighbour_Territory) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results_Trans <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Country_Territory","Neighbour_Territory")
    ) %>% 
    filter(Same_Nation == "No")

} # closes ifstatement for carmelia temporal files
# Load results for non transboundary (discrete) stocks
# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))
# 
# head(World_EEZs)

@@

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory)),
    Trans_Rate = n_trans/n_countries
    )
  # filter(Model_Index == 100)
  # head(Results_Data)

@@

Discrete_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_no_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbour_Territory))
  )

@@

## Validate Results using RFMOs

```{Validation_RFMOs}

#### Load RFMO data provided by Vicky (SAU)

RFMOs_sf <- fread(paste(Data_Path,"Spatial_Data/SAU_RFMO/SAU_RFMO_Sept_2015.shp",sep=""))

@@

## Analysis per Country

```{Tran_country_Map, eval =F, echo =F}

pal <- wes_palette("Zissou1", 1000, type = "continuous")

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_trans)) +
  scale_fill_gradientn(colours = pal,
                       na.value = "white") +
  ggtheme_map() +
  facet_wrap(~Model)

ggsave("R4_100_25.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@

# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Country_Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  "EBImage", #for reading images to the circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  "ggrepel", # for nice plot labels
  "ggsflabel", # for nice sf_plots labels
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase" # for species ecosystem affinity
)

@@

### Sub Routine; Neighbours

@@

### Estimate Transboundary Species

#### Function `GetSppDist`

@@

#### Function `EstTransIndex`

##### NOTES:

###### General:
- For now using SAU_C as presence absence
- Grouping by species distribution within EEZ and not EEZ area

###### Tresholds:
###### Model Index, line ~479

@@

###### Distribution Index, line ~482

@@

#### Function 'Mclapply_Hack'

@@

## Principal Routine

#### Control Pannel

@@

# Set Jurisdiction to EEZ or RFMO
Jurisdiction <- "RFMO"

@@

#### Run Routine
```{r Routine_parallel, eval = F, echo = F}

@@

## Sub Routine; SAU Catch

###`getSAucat`

```{r getSAUCatch, eval = F, echo = F}

# Function to get sau Catch data and total per country over a mean of (standarized 10 years )
getSAUCatch <-function(TaxonKey, Coord, nyears = 10){
  suppressMessages(

  year <- 67-nyears-1

Catch_Data <- GetSppDist(TaxonKey,Model="SAU_C",Coord = Coord) %>% 
  select(year:67) %>% 
  gather("Year","Catch",1:nyears) %>% 
  filter(!is.na(Catch)) %>%  # remove NAs earlier
  left_join(Index_Code,
            by ="INDEX") %>% 
  group_by(Species,Territory,Year) %>% 
  summarise(Total_Catch = sum(Catch,na.rm=T)) %>% 
  group_by(Species,Territory) %>% 
  summarise(Mean_Catch = mean(Total_Catch,na.rm=T))
)
return(Catch_Data)

#### Run Subroutine

```{r SAU_Catch_Data, eval = F, echo = F}

# get SAU catch data per species per nation

# Data needed for function
CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
  mutate(INDEX = seq(1,259200,1))

EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

  # Get list of species catch
Trans_Spp_List <- unique(Clean_Results_Trans$TaxonKey)

# Run routine and save it for latter
Sau_Catch_Data <- bind_rows(mclapply(Trans_Spp_List, getSAUCatch, Coord=CoorG))

write.csv(Sau_Catch_Data,
          paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep=""),
          row.names = F)

@@

## Load Results data

@@

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  select(Territory = Country.or.Area,
         georegion = Region.Name)

# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
# #The File
fnam_world_land <- "ne_50m_admin_0_countries.shp"

World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(Territory = NAME)

# head(World_land_sf)
# Transboundary Results ####

# For Carmelia
if(Jurisdiction == "EEZ"){
  if(Sys.info()[7] == "carmelia"){
    Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
  }else{
    # Read Sau Catch Data
    Sau_Catch_Data <- fread(paste(Results_Path,"Speceies_Data/Sau_Catch_Data.csv")) %>% 
      filter(!is.na(Territory))
    # For Hall and The Beast
    # List of species
    Spp <- list.files(Results_Path)[1:672]

    # Get resukts for all species
    Results_Trans <- GetTransResults(Spp)

    # Clean out countries that share with their own borders (Will be outdated soon)
    Auto_Remove_Territories <- Results_Trans %>%   
      rename(FishingRegion=Country_Territory) %>% 
      left_join(Clean_sau_eez_fes,
                by = "FishingRegion") %>% 
      select(TaxonKey,
             Country_Territory= FishingRegion,
             FishingRegion=Neighbor_Territory, #Neighbour_Territory
             Model_Index,
             Area_Index,
             CT_fishing_entity= fishing_entity) %>% 
      left_join(Clean_sau_eez_fes,
                by = "FishingRegion") %>% 
      select(1,2, 
             Neighbor_Territory = FishingRegion,
             Model_Index:CT_fishing_entity,
             NT_fishing_entity= fishing_entity,
             everything()) %>% 
      mutate(
        CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
        NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
        Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
      )

@@

    Territories_to_Remove <- Results_Trans %>% 
      filter(
        Country_Territory %in% Islands_to_Remove |
          Neighbor_Territory %in% Islands_to_Remove |
          Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
          Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
          Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
          Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
          Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
          Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
          Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
          Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
          Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
          Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
          Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
          Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
          Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
          Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
          Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
          Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
          Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
          Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
          Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
          Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
          Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
          Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
          Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
          Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
          Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
          Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
          Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
      ) %>%
      group_by(Country_Territory,Neighbor_Territory) %>% 
      summarise(n())

    # Cleaned results 
    Clean_Results_Trans <- Auto_Remove_Territories %>% 
      anti_join(Territories_to_Remove,
                by = c("Country_Territory","Neighbor_Territory")
      ) %>% 
      filter(Same_Nation == "No") %>% 
      rename(Territory = Country_Territory,
             Neighbour = Neighbor_Territory)

@@

    # The path
    path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
    # #The File
    fnam_world <- "SAUEEZ_July2015.shp"
    # #Load it!

    ### Sau Catch Data

    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), deader = TRUE)

  } # closes ifstatement for carmelia temporal files
}else{ # Closes EEZ ifelse

  # List of files without the non-trans data file
  Spp <- list.files(Results_Path)
  Spp <- Spp[Spp !="Non_Transboundary_Data.csv"]

  # Results loaing 
  Results_Trans <- GetTransResults(Spp)

  # Cleaning results (No cleaning needed for now)
  Clean_Results_Trans <- Results_Trans

  # Load results for non transboundary (discrete) stocks
  Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey))

  # Shapefiles 
  path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO/",sep="")
  # #The File
  fnam_world <- "SAU_RFMO_Sept_2015.shp"

#  GLobal data depending on jursidiction
# Load Regional shapefiles 
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

@@

## Determine Tresholds

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

Discrete_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_no_discrete_spp = length(unique(TaxonKey)),
    n_Territories = length(unique(Territory))
    )

@@

## Results per Territory

### Map of Transboundary Species

```{r Territory_Map, eval =F, echo =F}

World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000,2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T))

World_sf_si_land <- World_land_sf %>%
  # st_transform(crs = 4326) %>% # 4326
  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Catch_Country, by ="Territory") # Include total specices catch

# head(World_sf_si)s

# Create a pellet for plotting
# pal <- wes_palette("Zissou1", 1000, type = "continuous")

World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 5)
World_sf_si_land$BinsLan <- cut(World_sf_si_land$Total_Catch,breaks = 6)

unique(World_sf_si$Bins)
unique(World_sf_si_land$Bins)

# levels(World_sf_si$Bins)
# levels(World_sf_si_land$Bins_C)

Plot <- ggplot() +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour="white") + # n_trans_spp or Bins
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan),show.legend = FALSE) +
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  #                              rev(wes_palette(n = 4, name = "Darjeeling1"))
  #                              ),
  #                    na.value = "white"
  # ) +
  scale_fill_manual(values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#00A08A","#FF0000","#FF0000"),
                     na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Land.png", sep = "")

ggsave(Plot_Name,
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@

### OHI-inspired Circular plot Countries

```{r species_circluar_plot, eval = F, echo =F}

Countries_Data <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Territory = CT_fishing_entity) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(group = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,group) %>% 
  summarise(Total_Catch = sum(value,na.rm=T)) %>% 
  arrange(group,Total_Catch) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,group,value=Total_Catch)

# hist(Countries_Data$value)
# unique(Countries_Data$group)
Median_trans <- median(Countries_Data$value,na.rm=T)
Char <- as.factor(Countries_Data$group)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- length(unique(Countries_Data$group))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Countries_Data)) )
colnames(to_add) <- colnames(Countries_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Countries_Data <- bind_rows(Countries_Data, to_add)
Countries_Data <- Countries_Data %>% arrange(group,value)
Countries_Data$id <- seq(1, nrow(Countries_Data))

# Get the name and the y position of each label
label_data <- Countries_Data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- Countries_Data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]

# Make the plot
ggplot(Countries_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 4, name = "Darjeeling2")
                               ),
                     na.value = "white"
  ) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Countries_Data$id),4),
           y = c(20, 40, 60, 80,100),
           label = c("20", "40", "60"),
           color="grey", 
           size=3 , 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  ylim(-100,200) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  geom_text(data=label_data, 
            aes(x=id, y=110,
                label=individual,
                hjust=hjust), 
            color="black",
            # fontface="bold",
            alpha=0.6,
            size=2.5,
            angle= label_data$angle,
            inherit.aes = FALSE ) +
  geom_text(aes(x = 229, 
                y = 14,
                label = "Median"),
            colour = "grey", 
            size = 2.5,
            alpha=0.6,
            angle=5,
            inherit.aes = FALSE) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
                   ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE)

ggsave(
    plot = last_plot(),
    width = 14,
    height = 10,
    units = "in",
    filename = "Territory_circular_over10.tiff",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

@@

# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

@@

### OHI-inspired Circular plot Species

```{r species_circluar_plot, eval = F, echo =F}

Species_Data <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(n_trans_spp = length(unique(Territory))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = TaxonName) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag))) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value) %>% 
  filter(value > 10)

Median_trans <- median(Species_Data$value)
# hist(Species_Data$value)
# unique(Species_Data$group)

Char <- as.factor(Species_Data$group)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 8
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,value)
Species_Data$id <- seq(1, nrow(Species_Data))

# Get the name and the y position of each label
label_data <- Species_Data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- Species_Data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]

# Make the plot
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 4, name = "Darjeeling2")
                               ),
                     na.value = "white"
  ) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_hline(yintercept = Median_trans, colour = "black", alpha=1, size=0.3,linetype="dashed") +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),5),
           y = c(20, 40, 60, 80,100),
           label = c("20", "40", "60", "80","100"),
           color="grey", 
           size=3 , 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  ylim(-100,200) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  geom_text(aes(x = 229, 
                y = 14,
                label = "Median"),
            colour = "grey", 
            size = 2.5,
            alpha=0.6,
            angle=5,
            inherit.aes = FALSE) +
  geom_text(data=label_data, 
            aes(x=id, y=110,
                label=individual,
                hjust=hjust), 
            color="black",
            # fontface="bold",
            alpha=0.6,
            size=2.5,
            angle= label_data$angle,
            inherit.aes = FALSE ) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
                   ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE) +
  coord_polar()
